\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-18 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added qr code to gif
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59759 15284696-431f-4ddb-bdfa-cd5b030d7da7
Lidar, improved vector modules
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59781 15284696-431f-4ddb-bdfa-cd5b030d7da7

\blocknode{Lidar}{
\smallskip
The Lidar library ({\url {www.liblas.org}}) included in GRASS GIS permits the import of Lidar (.las)
data in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). 
Author Markus Metz tested r.in.lidar with a 705Gb .las file. \newline
On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
\begin{center}
 %\includegraphics[width=0.4\textwidth]{images/ofs1}
 %\newline
 %Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]

@@

\begin{itemize}
 \item {\bf v.} blabla
 \item {\bf v.} blabla
 \item {\bf v.} blabla
 \item {\bf v.} blabla
 \item {\bf v.} blabla
\end{itemize}
}

@@

\begin{center}
\includegraphics[width=\textwidth]{images/particles}
\end{center}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);

>>>>

\blocknode{Lidar}{
\smallskip
The Lidar library ({\url {www.liblas.org}}) used by GRASS GIS permits the import of LAS Lidar
data. The imported data can be in raster (r.in.lidar using statistics of choice) or in vector format (v.in.lidar). \newline
On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology
of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [8].\newline
\begin{center}
 %\includegraphics[width=0.4\textwidth]{images/ofs1}
 %\newline
 %Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]

@@

\begin{itemize}
 \item {\bf v.distance:} Calculates distances from points, lines, or areas to points, lines, or areas.
 \item {\bf v.overlay:} The processing speed has been substantially improved.
 \item {\bf v.net.*:} All vector network analysis tools provide now fine control over node costs.
 \item {\bf v.voronoi:} New option to create Voronoi diagrams for areas.
 \item {\bf v.rectify:} Vector data can now be georeferenced using various methods for 2D and 3D coordinate transformation.
\end{itemize}
}

@@

\begin{center}
\includegraphics[width=\textwidth]{images/particles}%
\raisebox{0pt}[0pt][0pt]{\hspace{-3cm}\colorbox{white}{\includegraphics[width=3cm]{images/particles_qr_short}}}
\end{center}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);
